Evaluate PEER in each cohort and brain region

### 2021-03-04 combined_analysis/eval_resid_in_each.Rmd
PEER K = 60
update K = 50

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf combined_analysis/eval_resid_in_each_cache/
ml git pandoc R/3.6.3 # to get peer
git pull
R

@@

>>>>

cd /hpc/users/hoffmg01/work/CMC/covarr-de
# rm -rf combined_analysis/eval_resid_in_each_cache/
export R_LIBS=/hpc/users/hoffmg01/.Rlib/R_403
ml purge
ml git pandoc R/3.6.3 # to get peer
git pull
R

@@

  PEER_setNk(model,50)
